\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-07-29 NAR_DRAFT.tex
fixes

\begin{figure*}
  \begin{center}
  \includegraphics{figures/fig_wes.pdf}
  \end{center}
  \caption{Model performance on 100X simulated whole genome.
  \textbf{(a)} Precision recall curves and \textbf{(c)} Reciever operating characteristic curves for 3 mutation signatures.
  Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the \batcave model.
  A perfectly calibrated model would generate the diagonal line.\bkmcomment{change the axis on b and d to be the same as the steyerberg paper. much clearer}}
\label{NAR-wgs_fig}
\end{figure*}

>>>>

\begin{figure*}[t]
  \begin{center}
  \includegraphics{figures/aml_plot.pdf}
  \end{center}
  \caption{Model performance on 300X Whole leukemia genome.
  \textbf{(a)} Precision/recall curves and \textbf{(c)} Reciever operating characteristic curves.
  Distribution of estimated true positive probabilities for true positive (top) and true negative (bottom) variants for \textbf{b)} the MuTect model and \textbf{d)} the Calibrated model.
  A perfectly calibrated model would generate the diagonal line.}
  \label{NAR-aml}
\end{figure*}
